What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-05 icpc/icpc2010.tex
more migod edits

\end{abstract}
%\XXX{abstract too abstract}

@@

Topics in this paper and the previous paper are word bags or word distributions. These word distributions are found via Latent Dirichlet Allocation~\cite{Blei2003}, which finds independent word distributions shared among documents (changelog comments). The unfortunate aspect of topics that are word distributions is that they lack the tangibility of a rose. They do not self identify themselves with their tangible properties. Topics have to be identified by interpreting the prevalent words in the word distribution and by inspecting related documents. This is impractical when one has to handle more than one hundred different topics. It would be nice if we could have automatic assistance to determine what the topic is about. This is the power of labelling and naming.

If a topic has a name or a label we immediately have a good idea of  what it is. In our case the name is the bit of information, the summary, that was missing from our topics to make them useful and complete. Although we are convinced that accurate naming is not completely feasible, so we have focussed on labelling topics by non-functional requirements.

@@

\begin{comment}
In this paper we use LDA to identify topics.  LDA works by creating topic models for each period. A topic model is a statistical summary of the important subjects for that dataset.  The input to the algorithm is a set of documents, with contents treated as a bag of words, and a parameter to set the number of topics to generate. The algorithm returns a word-document matrix relating the occurrence frequency of a 
 The idea is similar to other IR approaches like TF/IDF (term frequency/inverse document frequency), which find uncommon words that aren't found in other wordlists. These approaches are unsupervised in that they rely solely on the source data with no human intervention.
\end{comment}

@@

%\XXX{how many do we have}
We wanted to compare two mature software projects, that had open repositories, within the same application domain. This allows us to partially control for differences in functional requirements. We selected MySQL and MaxDB, open-source, near-commercial quality database software. MaxDB started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project has 940 thousand lines of C source code~\footnote{generated using David A. Wheeler's \emph{SLOCCount}.}.
%How many developers?
%There are approximately ... developers working on it. 
The MySQL project started in 1994 but MySQL 3.23 was released in early 2001. MySQL contains 320 thousand lines of C and C++ source code.

@@

Our second list, \textsf{exp2}, relied on the ISO quality model (ISO9126)~\cite{iso9126}. It describes six high-level quality requirements (listed in Table \ref{tbl:wnsig}). There is some debate about the significance and importance of the terms in this model. However, it is ``an international standard and thus provides an internationally accepted terminology for software quality \cite[p. 58]{Bøegh2008},'' which is sufficient for the purposes of this research. However, these terms may not capture all words associated with the labels.  For example, the term ``user friendly'' is one most would agree is relevant to discussion of usability, but is not in the standard. Therefore we took the words from the taxonomy and expanded them.

@@

For the third -- \textsf{exp3} -- list of quality labels, we extended the list from \textsf{exp2} using unfiltered Wordnet similarity matches. Similarity in Wordnet means siblings in a hypernym tree. We do not include these words here for space considerations (but see the Appendix for our data repository). It isn't clear the words associated with our labels are specific enough, however: for example, the label \emph{maintainability} is associated with words \emph{ease} and \emph{ownership}.

@@

\XXX{this table should have mysql}
\begin{table}
	\caption{Automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table}

@@

It seems like the smaller the label the harder it is to get accurate results. Although these results seem better than our previous word bag results of \textsf{exp2} and \textsf{exp3}.

@@

\XXX{What are some words that these classifiers liked?}

\XXX{Summarize the numeric results, is it good/bad}

@@

We found that the multilabel learners of BR, CLR and HOMER did not do as well for Macro-ROC and Micro-F1 as NaiveBayes and other NaiveBayes derived learners did. This suggests that by sticking together multiple NaiveBayes leaners we could probably label topics effectively, but it'd require a separate NaiveBayes learner per label.

@@

%\subsection{Topic change over time}

%\XXX{I don't know!}

@@

%\XXX{Discuss how these are CHEAP techniques and although somewhat %inaccurate they don't require a tonne of work}

@@

% \XXX{Boost/COmbine wordbag w/ bayes}

>>>>

\end{abstract}

@@

Topics in this paper and the previous paper are word bags or word distributions. These word distributions are found via Latent Dirichlet Allocation~\cite{Blei2003}, which finds independent word distributions shared among documents (changelog comments). The unfortunate aspect of topics that are word distributions is that they lack the tangibility of a rose. They do not self identify with their tangible properties. Topics have to be identified by interpreting the prevalent words in the word distribution and by inspecting related documents. This is impractical when one has to handle more than one hundred different topics. It would be nice if we could have automatic assistance to determine what the topic is about. This is the power of labelling and naming.

%If a topic has a name or a label we immediately have a good idea of  %what it is. In our case the name is the bit of information, the %summary, that was missing from our topics to make them useful and %complete. Although we are convinced that accurate naming is not %completely feasible, so we have focussed on labelling topics by %non-functional requirements.

A topic --- that is, a word distribution in our world --- needs a suggestive name to succinctly convey its intent, and make it easy to use in discussions and analyses about the development of the system. Our previous experience leads us to believe that automated topic naming is currently infeasible in the general case, so we have decided to focus on topic labels from the sub-domain of non-functional requirements related to software quality.

@@

\begin{comment}
In this paper we use LDA to identify topics.  LDA works by creating topic models for each period. A topic model is a statistical summary of the important subjects for that dataset.  The input to the algorithm is a set of documents, with contents treated as a bag of words, and a parameter to set the number of topics to generate. The algorithm returns a word-document matrix relating the occurrence frequency of a 
 The idea is similar to other IR approaches like TF/IDF (term frequency/inverse document frequency), which find uncommon words that are not found in other wordlists. These approaches are unsupervised in that they rely solely on the source data with no human intervention.
\end{comment}

@@

To evaluate our approach, we sought candidate systems that were
mature projects and had openly accessible artifact repositories.
We also decided to select systems from the same application
domain, as we felt the functional requirements would probably be
broadly similar.
%We wanted to compare two mature software projects, that had open %repositories, within the same application domain. 
% This allows us to partially control for differences in functional %requirements. 
We selected MySQL and MaxDB as they were open-source, partially-commercial database systems. MaxDB started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project has 940 thousand lines of C source code~\footnote{generated using David A. Wheeler's \emph{SLOCCount}.}.
%How many developers?
%There are approximately ... developers working on it. 
The MySQL project started in 1994 but MySQL 3.23 was released in early 2001. MySQL contains 320 thousand lines of C and C++ source code.

@@

Our second list, \textsf{exp2}, relied on the ISO quality model (ISO9126)~\cite{iso9126}. ISO9126 describes six high-level quality requirements (listed in Table \ref{tbl:wnsig}). 
%There is some debate about the significance and importance of the %terms in this model. 
%However, it is ``an international standard and thus provides an %internationally accepted terminology for software quality \cite[p. %58]{Bøegh2008},'' which is sufficient for the purposes of this %research. 
ISO9126 is ``an international standard and thus provides an internationally accepted terminology for software quality \cite[p. 58]{Bøegh2008},'' that is sufficient for the purposes of this research.
However, the terms extracted from ISO9126 may not capture all words associated with the labels.  For example, the term ``redundancy'' is one most would agree is relevant to discussion of reliability, but is not in the standard. Therefore we took the words from the taxonomy and expanded them.

@@

For the third -- \textsf{exp3} -- list of quality labels, we extended the list from \textsf{exp2} using unfiltered Wordnet similarity matches. Similarity in Wordnet means siblings in a hypernym tree. We do not include these words here for space considerations (but see the Appendix for our data repository). It is not clear the words associated with our labels are specific enough, however: for example, the label \emph{maintainability} is associated with words \emph{ease} and \emph{ownership}.

@@

%\XXX{this table should have mysql}
\begin{table}
	\caption{Automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table}

@@

It seems like the smaller the label the harder it is to get accurate results. Although these results seem better than our previous word bag results of \textsf{exp2} and \textsf{exp3} because the ROC values are sufficiently higher in most cases other than MaxDB reliability and MySQL efficiency.

@@

@@

We found that the multilabel learners of BR, CLR and HOMER did not do as well for Macro-ROC and Micro-F1 as NaiveBayes and other NaiveBayes derived learners did. This suggests that by sticking together multiple NaiveBayes leaners we could probably label topics effectively, but it would require a separate NaiveBayes learner per label.

@@

MySQL and MaxDB's machine learners did dispatch off of some shared words. Words that were used to classify topics that were shared between MySQL and MaxDB included: bug, code, compiler, database, HP UX, delete, memory, missing, problems, removed, add, added, changed, problem, and test. Potentially adding these words to the word bags of \textsf{exp2} and \textsf{exp3} could improve performance while still being domain specific.

\begin{comment}
 shared-report.sh ; cat output/shared-j48-words

      2 bug
      2 code
      2 compiler
      2 database
      2 Delete_
      2 HP_UX
      2 memory
      2 missing
      2 monty_mysql_com
      2 monty_mysql_fi
      2 problems
      2 Removed
      2 work__home_bk_mysql
      4 4_0
      4 Add
      4 added
      4 Changed
      4 problem
      6 Added
      6 test

@@

%{Discuss how these are CHEAP techniques and although somewhat %inaccurate they don't require a tonne of work}

@@
